Rectangulotopes

### 2024-10-25 draft/rectangulotopes.tex
last two comments of ref X

>>>>

\cref{lem:yincount} and \cref{lem:whentosum} together already provide a realization of the quotientopes of the yin congruence, the vertices of which are in bijection with rectangulations that avoid one of the two patterns defining diagonal rectangulations~\cite{ACFF24}, and with $2\underline{41}3$-avoiding permutations, as mentioned in \cref{subsec:yinYangArcs}.
